Are Transformed Low Discrepancy Points Also Low Discrepancy?

### 2019-05-20 InvPts_verB.tex
Updates from Overleaf

Changing perspectives slightly, if $F_\unif'$ denotes the uniform distribution on the cube of volume one centered at the origin, $(-\boldsymbol{0.5},\boldsymbol{0.5})^d$, and the design $\Udes'$ is constructed by  subtracting $\boldsymbol{0.5}$ from each point in the design $\Udes$:
\begin{equation} \label{eq:Updef}
    \Udes' = \{\vu -\boldsymbol{0.5} : \vu \in \Udes \},
\end{equation}
then 
\begin{equation} \label{eq:desEquiv}
     D(\Udes',F'_\unif,K) = D(\Udes, F_\unif, K_\unif),
\end{equation}
where $K$ is the kernel defined above in \eqref{eq:OrigKernel}.  Recall that the origin is a special point in the definition of the inner product corresponding to this $K$ as a reproducing kernel in \eqref{eq:inner}.

>>>>

Changing perspectives slightly, if $F_\unif'$ denotes the uniform distribution on the cube of volume one centered at the origin, $(-0.5,0.5)^d$, and the design $\Udes'$ is constructed by  subtracting $\boldsymbol{0.5}$ from each point in the design $\Udes$:
\begin{equation} \label{eq:Updef}
    \Udes' = \{\vu -\boldsymbol{0.5} : \vu \in \Udes \},
\end{equation}
then 
\begin{equation} \label{eq:desEquiv}
     D(\Udes',F'_\unif,K) = D(\Udes, F_\unif, K_\unif),
\end{equation}
where $K$ is the kernel defined above in \eqref{eq:OrigKernel}.  Recall that the origin is a special point in the definition of the inner product corresponding to this $K$ as a reproducing kernel in \eqref{eq:inner}.
